paper3

### 2022-12-02 LCA-GB.Rmd
20221202

```{r}
# Model evaluation
#predicted = predict(xgb_tune, x_test)
# Predict outcomes with the test data
Test %>% dplyr::select(Sce, Abs, Nat, Rem, Rug) %>%
  st_drop_geometry() %>% 
  as.matrix() %>% 
  xgb.DMatrix() %>%
  predict(xgb_tune, ., reshape = T) %>%
  plyr::mapvalues(from = c(1, 2, 3, 4), to = c("Low", "Moderate", "High", "Outstanding")) %>%
  data.frame(predict = .) %>%
  data.frame(actual = plyr::mapvalues(Test$SQ, from = c(1, 2, 3, 4), to = c("Low", "Moderate", "High", "Outstanding")),
             predict = .) ->
  result

# confusion matrix
confusionMatrix(result$actual, result$predict) %>% print()

# Reference
# https://datascienceplus.com/extreme-gradient-boosting-with-r/

hex.2k$SQ.pred <-
  hex.2k %>%
  st_drop_geometry() %>%
  dplyr::select(Sce, Abs, Nat, Rem, Rug) %>%
  predict(xgb_tune, ., reshape = T) %>%
  plyr::mapvalues(from = c(1, 2, 3, 4), to = c("Low", "Moderate", "High", "Outstanding")) %>%
  as.factor()
```

# Visualisation

```{r}
theme_map <- function(...) {
  theme_minimal() +
    theme(
      text = element_text(family = "Arial", color = "#22211d"), #"Ubuntu Regular"
      axis.line = element_blank(),
      axis.text.x = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks = element_blank(),
      axis.title.x = element_blank(),
      axis.title.y = element_blank(),
      # panel.grid.minor = element_line(color = "#ebebe5", size = 0.2),
      panel.grid.major = element_blank(), #element_line(color = "#ebebe5", size = 0.2),
      panel.grid.minor = element_blank(),
      plot.background = element_blank(), #element_rect(fill = "#f5f5f2", color = NA), 
      panel.background = element_blank(), #element_rect(fill = "#f5f5f2", color = NA), 
      legend.background = element_blank(), #element_rect(fill = "#f5f5f2", color = NA),
      panel.border = element_blank(),
      ...
    )
}

p <- ggplot(hex.2k) +
  # municipality polygons
  geom_sf(aes(fill = SQ.pred), color = NA) +
  theme_map() +
  labs(x = NULL, y = NULL, 
       title = "Predicted scenic quality") +
  theme(legend.position = "bottom",
        title =element_text(size = 15)) +
  scale_fill_manual(
  # in manual scales, one has to define colors, well, manually
  # I can directly access them using viridis' magma-function
  values = RColorBrewer::brewer.pal(4, "YlOrBr"), #rev(magma(9)),
  #breaks = brks_scale,
  name = "Quality levels",
  drop = FALSE,
  labels = c("Low", "Moderate", "High", "Outstanding"),
  guide = guide_legend(
    direction = "horizontal",
    keyheight = unit(6, units = "mm"),
    keywidth = unit(30 / length(labels), units = "mm"),
    title.position = 'top',
    title.theme = element_text(size = 15),
    # I shift the labels around, the should be placed 
    # exactly at the right end of each legend key
    # title.hjust = -0.9,
    label.hjust = 0.2,
    label.theme = element_text(size = 12),
    nrow = 1,
    byrow = T,
    # also the guide needs to be reversed
    reverse = F,
    label.position = "bottom")
  )

plot(test[, "SQ"])
```

>>>>

\`\`\`{r} \# Model evaluation #predicted = predict(xgb_tune, x_test) \# Predict outcomes with the test data Test %\>% dplyr::select(Sce, Abs,

### 2022-12-02 paper3.Rmd
20221202

LANDMAP <- st_transform(LANDMAP, crs = st_crs(Wildness)) %>%
  exact_extract(Wildness, ., 
                fun = c('mean', 'median', 'coefficient_of_variation', 'variance', 'quantile'), 
                quantiles = c(0.25, 0.75)) %>%
  mutate(Wildness.mean = mean,
         Wildness.median = median,
         Wildness.iqr = q75 - q25,
         Wildness.cv = coefficient_of_variation,
         Wildness.variance = variance) %>%
  dplyr::select(-c(mean, median, q25, q75, coefficient_of_variation, variance)) %>%
  bind_cols(LANDMAP, .) %>%
  st_transform(crs = 27700)

landmap <- st_cast(LANDMAP, "POLYGON") %>%
  dplyr::mutate(UID = row_number(),
                x_coord = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 1],
                y_coord = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 2])
summary(landmap)
```

Separate the consultant and then split train-test sets
```{r}
landmap_A = landmap %>% filter(Consultant == "A")
landmap_B = landmap %>% filter(Consultant == "B")

@@

X_train <- train_set %>% 
  dplyr::select(Scenicness = Scenicness.weighted_bayescore,
                Wildness = Wildness.median, 
                x_coord, y_coord)
 X_test <-  test_set %>% 
   dplyr::select(Scenicness = Scenicness.weighted_bayescore,
                 Wildness = Wildness.median, 
                 x_coord, y_coord)

@@

scale_mapper = {'Low': int(0),
                'Moderate': int(1),
                'High': int(2),
                'Outstanding': int(3)}
y_train[['ScenicQuality']] = y_train[['ScenicQuality']].replace(scale_mapper).astype('int')
 y_test[['ScenicQuality']] = y_test[['ScenicQuality']].replace(scale_mapper).astype('int')
```
## Hyperparameter Tuning

@@

# -- try previous combinations of hyperparameter set
# Consultant A
# param_space = {
#            'booster': 'gbtree',
#    'num_boost_round': 209.910,
#                'eta': 0.451,
#              'gamma': 0,
#          'max_depth': 12,
#   'min_child_weight': 0.2,
#          'subsample': 0.758,
#   'colsample_bytree': 1,
#          'num_class': 4,
#          'objective': 'multi:softmax',
#        'eval_metric': 'merror',
#               'seed': 2046
#     }

@@

## Confusion matrix and its visualisation
```{python}
from sklearn.metrics import confusion_matrix, ConfusionMatrixDisplay
import matplotlib.pyplot as plt

@@

for j in range(len(shap_values)):
    ax = ax.ravel()
    # X.plot(ax=ax[j],column = shap_values.values[:,j],legend=True,
    #              vmin=-0.8,vmax=0.8,cmap=shap.plots.colors.red_white_blue)
    fig[j] = shap.summary_plot(shap_values[1],
                              X.values,
                              feature_names = X_vars,
                              show = False),
                              # plot_type = 'compact_dot', # making the dots disappear
                              plot_size = (50, 6))
             plt.gcf().axes[-1].set_aspect('auto')
             plt.tight_layout()
             plt.gcf().axes[-1].set_box_aspect(40)
    ax[j].set_title("SHAP for\n" + X_vars[j],fontsize=10)

@@

shap.summary_plot(shap_values[1],
                  X.values,
                  feature_names = ['Scenicness', 'Wildness', 'x_coord', 'y_coord'], show = False),
                  # plot_type = 'compact_dot', # making the dots disappear
                  plot_size = (50, 6))
plt.gcf().axes[-1].set_aspect('auto')
plt.tight_layout()
plt.gcf().axes[-1].set_box_aspect(40) # smaller "box_aspect" value to make colorbar thicker
plt.show(); plt.close()
# plt.savefig('fig_tes1.png', bbox_inches='tight',dpi=300); plt.close()
```
## Spatial patterns of SHAP values
```{r}
shap_values = py$shap_values
shap_Low = data.frame(shap_values[[1]]) %>% transmute(SHAP_Scenicness_Low = X1, 
                                                      SHAP_Wildness_Low = X2,
                                                      SHAP_Location_Low = X3 + X4) 
shap_Moderate = data.frame(shap_values[[2]]) %>% transmute(SHAP_Scenicness_Moderate = X1,
                                                           SHAP_Wildness_Moderate = X2,
                                                           SHAP_Location_Moderate= X3 + X4)
shap_High = data.frame(shap_values[[3]]) %>% transmute(SHAP_Scenicness_High = X1,
                                                       SHAP_Wildness_High = X2,
                                                       SHAP_Location_High = X3 + X4)
shap_Outstanding = data.frame(shap_values[[4]]) %>% transmute(SHAP_Scenicness_Outstanding = X1,
                                                              SHAP_Wildness_Outstanding = X2,
                                                              SHAP_Location_Outstanding = X3 + X4)

@@

```
## Visualising the spatial distributions of SHAP values for each covariate with each class
```{r}
library(ggplot2)

@@

## map together
setwd("Z:\\R\\R projects\\LCA-GB\\figures")
png(filename = "SHAP_values.png", w = 10*2, h = 6*2, units = "in", res = 300)
par(mar = c(0,0,0,0))
multiplot(list(f[1], f[2], f[3], f[4], 
               f[5], f[6], f[7], f[8], 
               f[9], f[10], f[11], f[12]), cols = 4)
dev.off()
```
# Change of support (to 1 km grid)
```{r}
# -- download OSGB 1 km grid from github and covert its coordinate system to 27700
grid_1km <- "https://raw.githubusercontent.com/charlesroper/OSGB_Grids/master/GeoJSON/OSGB_Grid_1km.geojson" |>
  geojsonio::geojson_read(what = "sp") |>
  as("sf") |>
  st_transform(crs = 27700)

@@

@@

# -- download the administrative region for Great Britain from GADM for subseting the 1 km grid
GB <- raster::getData('GADM', country = 'GBR', level = 1) |>
  as('sf') |>
  filter(!NAME_1=='Northern Ireland') |>
  st_union() |>
  st_transform(crs = 27700)
plot(GB)

grid_1km <- grid_1km[GB, ]
```
# prepare environment for running python
```{r}
Sys.setenv("RETICULATE_PYTHON" = ".\\.venv\\Scripts\\python.exe")
# Sys.getenv()
Sys.which("Python")

@@

# SHAP value
```{python plot}
import shap

@@

# landmap = r.landmap

# X_vars = ['Scenicness','Wildness', 'x_coord', 'y_coord']
# 
# import matplotlib.pyplot as plt
# 
# fig, ax = plt.subplots(2,2,figsize=(15,15))
# 
# for j in range(len(shap_values)):
#     ax = ax.ravel()
#     # X.plot(ax=ax[j],column = shap_values.values[:,j],legend=True,
#     #              vmin=-0.8,vmax=0.8,cmap=shap.plots.colors.red_white_blue)
#     fig[j] = shap.summary_plot(shap_values[1],
#                               X.values,
#                               feature_names = X_vars,
#                               show = False),
#                               # plot_type = 'compact_dot', # making the dots disappear
#                               plot_size = (50, 6))
#              plt.gcf().axes[-1].set_aspect('auto')
#              plt.tight_layout()
#              plt.gcf().axes[-1].set_box_aspect(40)
#     ax[j].set_title("SHAP for\n" + X_vars[j],fontsize=10)
#     
# fig.delaxes(ax[-1])
# 
# 
# shap.summary_plot(shap_values[1],
#                   X.values,
#                   feature_names = ['Scenicness', 'Wildness', 'x_coord', 'y_coord'], show = False),
#                   # plot_type = 'compact_dot', # making the dots disappear
#                   plot_size = (50, 6))
# plt.gcf().axes[-1].set_aspect('auto')
# plt.tight_layout()
# plt.gcf().axes[-1].set_box_aspect(40) # smaller "box_aspect" value to make colorbar thicker
# plt.show(); plt.close()
# plt.savefig('fig_tes1.png', bbox_inches='tight',dpi=300); plt.close()
```
## Spatial patterns of SHAP values
```{r}
shap_values = py$shap_values
shap_Low = data.frame(shap_values[[1]]) %>% transmute(SHAP_Scenicness_Low = X1, 
                                                      SHAP_Wildness_Low = X2,
                                                      SHAP_Location_Low = X3 + X4) 
shap_Moderate = data.frame(shap_values[[2]]) %>% transmute(SHAP_Scenicness_Moderate = X1,
                                                           SHAP_Wildness_Moderate = X2,
                                                           SHAP_Location_Moderate= X3 + X4)
shap_High = data.frame(shap_values[[3]]) %>% transmute(SHAP_Scenicness_High = X1,
                                                       SHAP_Wildness_High = X2,
                                                       SHAP_Location_High = X3 + X4)
shap_Outstanding = data.frame(shap_values[[4]]) %>% transmute(SHAP_Scenicness_Outstanding = X1,
                                                              SHAP_Wildness_Outstanding = X2,
                                                              SHAP_Location_Outstanding = X3 + X4)

grid_1km_shap = cbind(grid_1km, shap_Low, shap_Moderate, shap_High, shap_Outstanding)
rm(list = c('shap_Low', 'shap_Moderate', 'shap_High', 'shap_Outstanding'))
```
## plotting the spatial distribution of SHAP values
```{r}
library(ggplot2)

f2 <- list()

for (i in 1:12) {
  f2[[i]] <- ggplot() +
    geom_sf(data = grid_1km_shap, aes(fill = !!sym(names(grid_1km_shap)[i+11])), colour = NA) +
    theme_map() +
    labs(x = NULL, 
         y = NULL, 
         title = names(grid_1km_shap)[i+11]) + # stringr::str_c("SHAP for ", collapse = " ")
    theme(legend.position = "bottom",
          title = element_text(size = 15)) +
    scale_fill_gradient2(low = ("#CB181D"),
                         mid = "white",
                         name = NULL,
                         high = ("#2171B5"),
                         midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))
}

setwd("Z:\\R\\R projects\\LCA-GB\\figures")
png(filename = "SHAP_values_4.png", w = 10*2, h = 6*2, units = "in", res = 300)
par(mar = c(0,0,0,0))
multiplot(list(f2[1], f2[2], f2[3], f2[4], 
               f2[5], f2[6], f2[7], f2[8], 
               f2[9], f2[10], f2[11], f2[12]), cols = 4)
dev.off()
```

@@

plt.title('Feature Importances')
plt.barh(range(len(indices)), importances[indices], color='g', align='center')
plt.yticks(range(len(indices)), [features[i] for i in indices])
plt.xlabel('Relative Importance')
plt.show()

@@

```{python}
# get just the explanations for the positive class
# shap_values = shap_values[...,1]

# shap.plots.bar(shap_values[...,1])
```

```{python}
shap.initjs()
# shap_values[1] what does the index mean?
shap.summary_plot(shap_values[1], X_train.values, feature_names=X_train.columns)
# shap.summary_plot(shap_values, X_test, max_display = X_test.shape[1])

# -- Dependence Contribution Plots
# make plot.
shap.dependence_plot('Scenicness.median_of_bayescore', shap_values[3], X_train, interaction_index = 'Wildness.median')

# explainer = shap.TreeExplainer(model2)
# shap_values = explainer.shap_values(X_sampled)
# shap.summary_plot (shap_values, X_sampled, max_display=X_sampled.shape[1]) 
# i=2
# shap.force_plot(explainer.expected_value[0], shap_values[0][i], X_test.values[i], feature_names = X_test.columns)
# 
# 
# fig.set_size_inches(18.5, 20.5)
# fig.savefig("Z:\\R\\R projects\\LCA-GB\\models\\shap.png")
# 
# # -- first trial
# shap.initjs()
# shap_values = shap.TreeExplainer(model).shap_values(X_test)
# shap.summary_plot(shap_values, X_test)
# 
# # -- second trial
# scaler = StandardScaler()
# scaled_data = scaler.fit_transform(X_test.iloc[:,:-1])
# shap_values = explainer.shap_values(scaled_data.iloc[0,:-1].values.reshape(1,-1))
# shap.force_plot(explainer.expected_value[0], shap_values[0], link='logit')  # repeat changing 0 for i in range(0, 5)
# 
# # -- third trial
# shap.initjs()
# class_names = ['Low', 'Moderate', ' High', 'Outstanding']
# shap.summary_plot(shap_values, X_test, plot_type="bar", class_names= class_names, feature_names = ['Scenicness', 'Wildness'])
# 
# # -- plot the global importance of each feature
# shap.plots.bar(explainer)
# 
# # visualize the first prediction's explanation
# shap.force_plot(explainer.expected_value[0], shap_values[0])
# 
# # fig, ax = plt.subplots(figsize=(20, 20),dpi=200)
# # shap.summary_plot(shap_values)
# # # or 
# # shap.plots.beeswarm(shap_values)
# shap.summary_plot(shap_values[2], X_test)
# 
# # fig, ax = plt.subplots(figsize=(20, 20),dpi=200)
# shap.summary_plot(shap_values, X_test, plot_type="bar")
# 
# shap_interaction_values = shap.TreeExplainer(model).shap_interaction_values(X_train)
#     
# X_names = ['Scenicness.median','x_coord','y_coord']
# 
# shap.summary_plot(shap_interaction_values, X_train, max_display=15, 
#                   feature_names = X_names,
#                   plot_type = 'dot')
#                   # plot_type="compact_dot")
#                   
# import shap  # package used to calculate Shap values
# 
# # Create object that can calculate shap values
# explainer = shap.TreeExplainer(my_model)
# 
# # calculate shap values. This is what we will plot.
# # Calculate shap_values for all of val_X rather than a single row, to have more data for plot.
# shap_values = explainer.shap_values(val_X)
# 
# # Make plot. Index of [1] is explained in text below.
# shap.summary_plot(shap_values[1], val_X)                  
```

>>>>

LANDMAP <- st_transform(LANDMAP, crs = st_crs(Wildness)) %>%
  exact_extract(Wildness, ., 
                fun = c('mean', 'median', 'coefficient_of_variation', 'variance', 'quantile'), 
                quantiles = c(0.25, 0.75)) |>
  mutate(Wildness.mean = mean,
         Wildness.median = median,
         Wildness.iqr = q75 - q25,
         Wildness.cv = coefficient_of_variation,
         Wildness.variance = variance) |>
  dplyr::select(-c(mean, median, q25, q75, coefficient_of_variation, variance)) %>%
  bind_cols(LANDMAP, .) |>
  st_transform(crs = 27700)

landmap <- st_cast(LANDMAP, "POLYGON") |>
  dplyr::mutate(UID = row_number(),
                x_coord = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 1],
                y_coord = st_centroid(landmap$geometry) %>% st_coordinates() %>% .[, 2])
summary(landmap)

plot(st_centroid(landmap)[, 1])
plot(d[, 'centroids'], add = T, col = 'red', pch = 19)

test <- st_centroid(landmap)
  st_centroid() %>% 
  # this is the crs from d, which has no EPSG code:
  st_transform(., '+proj=longlat +ellps=GRS80 +no_defs') %>%
  # since you want the centroids in a second geometry col:
  st_geometry()
```

Separate the consultant and then split train-test sets

```{r}
landmap_A = landmap %>% filter(Consultant == "A")
landmap_B = landmap %>% filter(Consultant == "B")

@@

X_train <- train_set %>% 
  dplyr::select(Scenicness = Scenicness.weighted_bayescore,
                Wildness = Wildness.mean, 
                x_coord, y_coord)
 X_test <-  test_set %>% 
   dplyr::select(Scenicness = Scenicness.weighted_bayescore,
                 Wildness = Wildness.mean,
                 x_coord, y_coord)

@@

scale_mapper = {'Low': int(0),
                'Moderate': int(1),
                'High': int(2),
                'Outstanding': int(3)}

y_train[['ScenicQuality']] = y_train[['ScenicQuality']].replace(scale_mapper).astype('int')
 y_test[['ScenicQuality']] = y_test[['ScenicQuality']].replace(scale_mapper).astype('int')
```

## Hyperparameter Tuning

@@

# -- try previous combinations of hyperparameter set
# Consultant A
# param_space = {
#            'booster': 'gbtree',
#    'num_boost_round': 209.910,
#                'eta': 0.451,
#              'gamma': 0,
#          'max_depth': 12,
#   'min_child_weight': 0.2,
#          'subsample': 0.758,
#   'colsample_bytree': 1,
#          'num_class': 4,
#          'objective': 'multi:softmax',
#        'eval_metric': 'merror',
#               'seed': 2046}

@@

## Confusion matrix and its visualisation

```{python}
from sklearn.metrics import confusion_matrix, ConfusionMatrixDisplay
import matplotlib.pyplot as plt

@@

for j in range(len(shap_values)):
    ax = ax.ravel()
    # X.plot(ax=ax[j],column = shap_values.values[:,j],legend=True,
    #              vmin=-0.8,vmax=0.8,cmap=shap.plots.colors.red_white_blue)
    fig[j] = shap.summary_plot(shap_values[1],
                               X.values,
                               feature_names = X_vars,
                               show = False),
                               # plot_type = 'compact_dot', # making the dots disappear
                               plot_size = (50, 6))

             plt.gcf().axes[-1].set_aspect('auto')
             plt.tight_layout()
             plt.gcf().axes[-1].set_box_aspect(40) # smaller "box_aspect" value to make colorbar thicker
    ax[j].set_title("SHAP for\n" + X_vars[j],fontsize=10)

@@

# 
# shap.summary_plot(shap_values[1],
#                   X.values,
#                   feature_names = ['Scenicness', 'Wildness', 'x_coord', 'y_coord'], show = False),
#                   # plot_type = 'compact_dot', # making the dots disappear
#                   plot_size = (50, 6))
# plt.gcf().axes[-1].set_aspect('auto')
# plt.tight_layout()
# plt.gcf().axes[-1].set_box_aspect(40) 
# plt.show(); plt.close()
# plt.savefig('fig_tes1.png', bbox_inches='tight',dpi=300); plt.close()
```

## Spatial patterns of SHAP values

```{r}
shap_values = py$shap_values
shap_Low = data.frame(shap_values[[1]]) %>% transmute(SHAP_Scenicness_Low = X1, 
                                                      SHAP_Wildness_Low = X2,
                                                      SHAP_Location_Low = X3 + X4) 
shap_Moderate = data.frame(shap_values[[2]]) %>% transmute(SHAP_Scenicness_Moderate = X1,
                                                           SHAP_Wildness_Moderate = X2,
                                                           SHAP_Location_Moderate= X3 + X4)
shap_High = data.frame(shap_values[[3]]) %>% transmute(SHAP_Scenicness_High = X1,
                                                       SHAP_Wildness_High = X2,
                                                       SHAP_Location_High = X3 + X4)
shap_Outstanding = data.frame(shap_values[[4]]) %>% transmute(SHAP_Scenicness_Outstanding = X1,
                                                              SHAP_Wildness_Outstanding = X2,
                                                              SHAP_Location_Outstanding = X3 + X4)

@@

```

## Visualising the spatial distributions of SHAP values for each covariate with each class

```{r}
library(ggplot2)

@@

## map together
setwd("Z:\\R\\R projects\\LCA-GB\\figures")
png(filename = "SHAP_values.png", w = 10*2, h = 6*2, units = "in", res = 300)
par(mar = c(0,0,0,0))
multiplot(list(f[1], f[2], f[3], f[4], 
               f[5], f[6], f[7], f[8], 
               f[9], f[10], f[11], f[12]), cols = 4)
dev.off()
```

# Change of support (to 1 km grid)

```{r}
# -- download OSGB 1 km grid from github and covert its coordinate system to 27700
grid_1km <- "https://raw.githubusercontent.com/charlesroper/OSGB_Grids/master/GeoJSON/OSGB_Grid_1km.geojson" |>
  geojsonio::geojson_read(what = "sp") |>
  as("sf") |>
  st_transform(crs = 27700)

@@

rm('Wildness')

@@

# -- download the administrative region for Great Britain from GADM for sub-setting the 1 km grid
GB <- raster::getData('GADM', country = 'GBR', level = 1) |>
  as('sf') |>
  filter(!NAME_1=='Northern Ireland') |>
  st_union() |>
  st_transform(crs = 27700)
plot(GB)

grid_1km <- grid_1km[GB, ]

# -- remove the grid cells that lack of scenicness and wildness measures
grid_1km <- grid_1km[!is.na(grid_1km$Scenicness.weighted_bayescore), ] %>%
  .[!is.na(grid_1km$Wildness.median), ]
```

# prepare environment for running python

@@

# SHAP value

```{python plot}
import shap

@@

# The approximate argument set to True to fix some of the shap_values with NaN value
# shape of shap_values is : (4, 1321, 4) means 4 classes, 1321 rows(observations), each 4 columns(features).
shap_values = explainer.shap_values(X, approximate = True)
```

## Spatial patterns of SHAP values

```{r}
shap_values = py$shap_values
shap_Low = data.frame(shap_values[[1]]) %>% transmute(SHAP_Scenicness_Low = X1, 
                                                      SHAP_Wildness_Low = X2,
                                                      SHAP_Location_Low = X3 + X4) 
shap_Moderate = data.frame(shap_values[[2]]) %>% transmute(SHAP_Scenicness_Moderate = X1,
                                                           SHAP_Wildness_Moderate = X2,
                                                           SHAP_Location_Moderate= X3 + X4)
shap_High = data.frame(shap_values[[3]]) %>% transmute(SHAP_Scenicness_High = X1,
                                                       SHAP_Wildness_High = X2,
                                                       SHAP_Location_High = X3 + X4)
shap_Outstanding = data.frame(shap_values[[4]]) %>% transmute(SHAP_Scenicness_Outstanding = X1,
                                                              SHAP_Wildness_Outstanding = X2,
                                                              SHAP_Location_Outstanding = X3 + X4)

grid_1km_shap = cbind(grid_1km, shap_Low, shap_Moderate, shap_High, shap_Outstanding)
rm(list = c('shap_Low', 'shap_Moderate', 'shap_High', 'shap_Outstanding'))
```

## plotting the spatial distribution of SHAP values

```{r}
library(ggplot2)

for (i in 1:12) {
  f[[i]] <- ggplot() +
    geom_sf(data = grid_1km_shap, aes(fill = !!sym(names(grid_1km_shap)[i+11])), colour = NA) +
    theme_map() +
    labs(x = NULL, 
         y = NULL, 
         title = names(grid_1km_shap)[i+11]) + # stringr::str_c("SHAP for ", collapse = " ")
    theme(legend.position = "bottom",
          title = element_text(size = 15)) +
    scale_fill_gradient2(low = ("#CB181D"),
                         mid = "white",
                         name = NULL,
                         high = ("#2171B5"),
                         midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))
}

f[13] <- ggplot() +
  geom_sf(data = grid_1km_shap, aes(fill = !!sym(names(grid_1km_shap)[4])), colour = NA) +
  theme_map() +
  labs(x = NULL, 
       y = NULL, 
       title = names(grid_1km_shap)[4]) + # stringr::str_c("SHAP for ", collapse = " ")
  theme(legend.position = "bottom",
        title = element_text(size = 15)) +
  scale_fill_gradient2(low = ("#CB181D"),
                       mid = "white",
                       name = NULL,
                       high = ("#2171B5"),
                       midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))

f[14] <- ggplot() +
  geom_sf(data = grid_1km_shap, aes(fill = !!sym(names(grid_1km_shap)[6])), colour = NA) +
  theme_map() +
  labs(x = NULL, 
       y = NULL, 
       title = names(grid_1km_shap)[6]) + # stringr::str_c("SHAP for ", collapse = " ")
  theme(legend.position = "bottom",
        title = element_text(size = 15)) +
  scale_fill_gradient2(low = ("#CB181D"),
                       mid = "white",
                       name = NULL,
                       high = ("#2171B5"),
                       midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))

f[15] <- ggplot() +
  geom_sf(data = grid_1km_shap, aes(fill = !!sym(names(grid_1km_shap)[10])), colour = NA) +
  theme_map() +
  labs(x = NULL, 
       y = NULL, 
       title = names(grid_1km_shap)[10]) + # stringr::str_c("SHAP for ", collapse = " ")
  theme(legend.position = "bottom",
        title = element_text(size = 15)) +
  scale_fill_gradient2(low = ("#CB181D"),
                       mid = "white",
                       name = NULL,
                       high = ("#2171B5"),
                       midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))

f[16] <- ggplot() +
  geom_sf(data = grid_1km_shap, aes(fill = !!sym(names(grid_1km_shap)[11])), colour = NA) +
  theme_map() +
  labs(x = NULL, 
       y = NULL, 
       title = names(grid_1km_shap)[11]) + # stringr::str_c("SHAP for ", collapse = " ")
  theme(legend.position = "bottom",
        title = element_text(size = 15)) +
  scale_fill_gradient2(low = ("#CB181D"),
                       mid = "white",
                       name = NULL,
                       high = ("#2171B5"),
                       midpoint = 0,
                         space = "Lab",
                         na.value = "white",
                         guide = guide_colourbar(title.position = "top",
                                                 # title.hjust = 0.5,
                                                 title.vjust = 0.8,
                                                 barwidth = 15))

setwd("Z:\\R\\R projects\\LCA-GB\\figures")
png(filename = "SHAP_values_5.png", w = 10*2, h = 6*2, units = "in", res = 300)
par(mar = c(0,0,0,0))
multiplot(list(f[1], f[2], f[3], f[4], f[13],
               f[5], f[6], f[7], f[8], f[14],
               f[9], f[10], f[11], f[12], f[15]), cols = 5)
dev.off()
rm(c('i', 'f'))
```

#### Waiting for deletion -- The XGBoost built-in feature importance

@@

plt.title('Feature Importances')
plt.barh(range(len(indices)), importances[indices], color = 'g', align = 'center')
plt.yticks(range(len(indices)), [features[i] for i in indices])
plt.xlabel('Relative Importance')
plt.show()

@@

#### Waiting for deletion -- The dependence plots may not be used.

```{python}
shap.initjs()
# shap_values[1] what does the index mean?
shap.summary_plot(shap_values[1], X_train.values, feature_names = X_train.columns)
# shap.summary_plot(shap_values, X_test, max_display = X_test.shape[1])

# -- Dependence Contribution Plots
# make plot.
shap.dependence_plot('Scenicness.median_of_bayescore', shap_values[3], X_train, interaction_index = 'Wildness.median')
```
